\subsubsection*{Work History}
% \paragraph{Antecedentes Laborales:}
\begin{itemize}
	\item September 2010 - today: Kinetica Solutions.
		\subitem \underline{Tasks performed:}
		\begin{itemize}
			\item Design and implementation in C\# of a statistics system and a
				small backoffice; using MSSQL, MSMQ, WCF (both for IPC and
				REST webservices), and MVC.
			\item Design and implementation of a system to serve efficiently widgets with
				the information calculated by the previous system; using 
				C\#, WCF, MVC, jQuery, flot (a jQuery plugin for charting), 
				MongoDB and Memcache.
				\subitem All of the projects where developed using SCRUM, and with a
					strong emphasis on code quality and testing coverage.
			\item Two I+D projects: one on MongoDB (later expanded in the
				production of the latter project and another combining nUnit,
				Selenium and ImageMagick to add testability to the design
				of a site, i.e. to compare an implemented site and a model.
		\end{itemize}
	\item November 2009 - September 2010: Tecnopro
		\subitem \underline{Tasks performed:}
		\begin{itemize}
			\item Java Development customizing the IT and Management suite made by CA.
		\end{itemize}
	\item July 2007 -- November 2009: Recursiva
		\subitem \underline{Tasks performed:}
			\begin{itemize}
				\item Backend, frontend and web programming in C++, C\#, Java and MSSQL 
					using the usual frameworks: Spring/Spring.net, Unity, Hibernate/NHibernate,
					J/NUnit, WCF, MSMQ on Windows and Windows CE
			\end{itemize}

	\item March 2006 -- March 2007: Axxon Solutions
		\subitem \underline{Tasks performed:}
			\begin{itemize}
				\item Web Programming in PHP, ASP, Javascript and MySQL on Windows
			\end{itemize}

	\item September - October 2005: TIDA
		\subitem \underline{Tasks performed:}
			\begin{itemize}
				\item Web Programming in PHP on Linux, developing sites running on Mambo and Joomla
			\end{itemize}

	\item August 2004 - May 2005 : ATX -- Sondeos Global
		\subitem \underline{Tasks performed:}
			\begin{itemize}
				\item Web Programming in PHP and MySQL on Windows and Linux.
				\item Administration of the servers used
			\end{itemize}

	\item April-June 2004: SOCDUS, Odontol'ogic network.
		\subitem \underline{Tasks performed:}
			\begin{itemize}
				\item Data Entry y Auditor'ia de Fichas Odontol'ogicas
			\end{itemize}
\end{itemize}
